### 2015-03-26 tex/definitions.tex
Added proofs and definitions to ./tex/paper.tex to create an extended version of the paper. Numerous corrections to proofs.tex

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim$, is a function between binary relations. The functional applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
The bisimularity relation is the greatest fixed point of the functional.
\end{definition}

@@

>>>>

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim$, is a function between binary relations. The functional applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
The bisimilarity relation is the greatest fixed point of the functional.
\end{definition}

@@

\paragraph{Relationship between bisimulation and fix points}

If you have a lattice $L$, and you have some 
function $F$ which transforms one point on the lattice into another, then
$F$ is an endofunction on $L$. For any endofunction $F$, a 
a post-fixed point of $F$ is any point $x$ where $x < F(x)$, and a pre-fixed 
point is any point $x$ where $F(x) < x$. The inductively defined set $F_\mathit{ind}$
is equal to the meet of all the pre-fixed points, and the conductively 
defined set $F_\mathit{coind}$ is equal to the join of all post-fixed points. 
$x \leq F_\mathit{coins}$. If $F$ is monotone, then the greatest fixed point $\mathit{gfp}(F)$ 
is equal to the coinductive set, and the least fixed point $\mathit{lfp}(F)$ is equal to the 
inductive set.

For some monotone endofunction $F$, the inductive proof principle states that 
if $F(x) \leq x$, then $\mathit{lfp}(F) \leq x$. Similarly, the coinductive proof 
principle states that if $x \leq F(x)$, then $x \leq \mathit{gfp}(F)$.

Because the functional associated to bisimulation $F_\sim$ is monotone over 
the lattice formed by sets of pairs of states, we may invoke the coinductive proof principle
to identify post-fixed points of $\mathit{gfp}(F_\sim)$. It can be proved that
the greatest fixed point of the functional associated to 
bisimulation is equal to the bisimilarity relation $\sim = \mathit{gfp}(F_\sim)$, that 
all bisimulations are 
post-fixed points of $F_\sim$, and all post-fixed points of $F_\sim$ are 
bisimulations. Thus, we may invoke the coinductive proof principle to show that some relation $R$ is a bisimulation, by proving that $R$ is a pre-fixed point of $F_\sim$: $R \leq F_\sim(R)$.
